Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-02-16 AO_bondedSi.tex
SiGap_17 finalized, sample transport accessory text added, new pdfs made.
Analysis for zero gap, SiGaps_18 and 19.

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions}
		\label{figVG12_STA_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh}
                \label{figVG12_f50}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.
\label{figVG12}}
\end{figure}

@@

\subsection{Measurement of a sample with no implanted gaps}
We measured direct bonded Si$-$Si sample (part VG02, Table \ref{tbl_experiments}) with no intentionally embedded gaps.  We measured transmission spectra in four randomly chosen regions of the $100\;$mm bonded wafers, with no preparatory imaging available.  Two of the regions showed evidence of large ($>\lambda$) gaps.  The other two regions showed almost 100\% transmission, when normalized by measurements of $T_{DSP}$.  We apply our formalism to one of these regions to get an estimate for the smallest gap that we can constrain.  Figure \verb|\ref{fig_xxx}| shows a zoom in of the measured normalized transmission spectrum, which shows strongly correlated noise, especially in the wavelength range $2000-2500\;$nm.

>>>>

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.35\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions}
		\label{figVG12_STA_corner}
        \end{subfigure}
        \begin{subfigure}[b]{0.65\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh}
                \label{figVG12_f50}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.
\label{figVG12}}
\end{figure}

@@

\subsection{What is the smallest gap this technique can detect?}
We devised two experiments to approach the question, ``What is the smallest gap this technique can detect?''.  We applied our MCMC model fitting formalism to an unbonded DSP wafer.  The measured transmission spectrum was normalized by a transmission spectrum of the same sample taken only a few minutes earlier.  Any difference of this normalized transmission from unity is attributable entirely to measurement uncertainty, and represents the smallest possible signal one could extract.  We also measured bonded sample VG09-12 in a region away from the intentionally implanted gap.  This spectrum was processed in the same way as the spectra of the VG09-12 mesh area, exhibiting a mean value of 0.9998 and a standard deviation $\sigma=0.0008$.  This spectrum is consistent with no gap.  We applied our MCMC formalism to further constrain the range of gap sizes consistent with the spectrum.  Table \verb|\ref{tbl summary of gap fit extents}| summarizes the sizes of gaps.  The well-calibrated DSP noise spectrum rules out ($>3\sigma$) gap sizes larger than about 8.0 nm over $>80$\% of the measurement area.  Similarly, the VG09-12 off-mesh spectrum rules out gaps greater than 13 nm over $>80$\% of the measurement area.
